Demes: a specification for interchanging complex demography

### 2022-01-27 paper.tex
Various edits (#32)

Population sizes are given as the number of individuals.
\jkcomment{As opposed to genomes. Why did we do this?}
\aprcomment{With this, we might want to be able to specify ploidy in as
a graph-level option, which defaults to 2. That would make the reasons
behind this decision obvious then, I think.}
\krtcomment{The number of genomes can be a non-obvious function of the number of individuals, too.
Polymorphism for chromosome number, etc., are all real complications.}
Sizes and mating system details are specified for each population within
epochs. Epochs are contiguous time intervals that define
the existence interval of the population. Each epoch specifies the population size
over that interval, which can be a constant value or function defined by start
and end sizes that must remain positive.

Within a population, individuals are assumed to be exchangeable, but there are
also parameters for nonrandom mating, such as selfing or cloning rates, which
give the probability that offspring are generated from one generation to the
next by self-fertilisation or cloning of an individual. Cloning and selfing
rates can take any value between zero and one, and if both are specified then
the selfing rate is the probability an offspring is generated through
self-fertilisation given it was produced sexually (i.e. with probability one
minus the cloning rate). We omit any details regarding selection, as those would
fall outside the scope of demographic model specification, but...
\aprcomment{If selection is placed on top of the demographic model, this implies
that we are living in a soft selection world. Though sizes could just as easily
be interpreted as carrying capacities in a hard selection model.}
\krtcomment{We are firmly in the soft selection world here.  The connection to hard selection
requires some other strong assumptions that will sometimes be met, and sometimes not.
For example, if the mean fitnesses are approximately equal across demes, then a hard selection
model could be similar to a soft selection model.  Relevant literature to dig up: Felsenstein's review,
which will lead to other stuff.}

>>>>

Population sizes are given as the number of individuals.
We focus on the number of individuals as opposed to the number of genomes
in order to not limit other software (need term -- "consumers"?) by placing potentially arbitrary
restrictions on how the numbers of chromosomes, etc., vary amongst individuals.
\jkcomment{As opposed to genomes. Why did we do this?}
\aprcomment{With this, we might want to be able to specify ploidy in as
a graph-level option, which defaults to 2. That would make the reasons
behind this decision obvious then, I think.}
\krtcomment{The number of genomes can be a non-obvious function of the number of individuals, too.
Polymorphism for chromosome number, etc., are all real complications.}
\krtcomment{We support limited aspects of the mating system--more on this below.}
Sizes and mating system details are specified for each population within
epochs. Epochs are contiguous time intervals that define
the existence interval of the population. Each epoch specifies the population size
over that interval, which can be a constant value or function defined by start
and end sizes that must remain positive.

Within a population, individuals are assumed to be exchangeable, but there are
also parameters for nonrandom mating, such as selfing or cloning rates, which
give the probability that offspring are generated from one generation to the
next by self-fertilisation or cloning of an individual. Cloning and selfing
rates can take any value between zero and one, and if both are specified then
the selfing rate is the probability an offspring is generated through
self-fertilisation given it was produced sexually (i.e. with probability one
minus the cloning rate). We omit any details regarding selection.
Thus, the history of population size changes does not depend on mean fitnesses within
a population nor on differences in mean fitness between populations.
This indepedence of population size and selection is often called ``soft" selection \citep{christiansen1975hard}.

List of thoughts to turn into a paragraph:

\begin{enumerate}
    \item Selection parameters may be arbitrarily complex.  Different fitness effects in different demes.
          Variation over time.  Etc..
          The specification would become unwieldy and perhaps limiting.
    \item By allowing selfing and cloning, we allow many "standard" models to be considered with "no or little"
          extra effort.
    \item However, by parameterising selfing and cloning as we have, we are assuming that these properties of
          populations at given times can be specified independently from the genetics.
          In other words, mutations that cause selfing to "come and go" are not considered.
          However, consuming software is free to ignore these parameters and model the genetics within
          the framework of a soft selection model.
    \item We don't view these as limitations. Rather, this is what most people are doing most of the time.
          Just now we can finally try to do this part w/fewer errors.
\end{enumerate}

\aprcomment{If selection is placed on top of the demographic model, this implies
that we are living in a soft selection world. Though sizes could just as easily
be interpreted as carrying capacities in a hard selection model.}
\krtcomment{We are firmly in the soft selection world here.  The connection to hard selection
requires some other strong assumptions that will sometimes be met, and sometimes not.
For example, if the mean fitnesses are approximately equal across demes, then a hard selection
model could be similar to a soft selection model.  Relevant literature to dig up: Felsenstein's review,
which will lead to other stuff.}
